%-------------------------
% Resume in Latex
% Author: Matty
% Based on: https://github.com/jakegut/resume (which was itself based on https://github.com/sb2nov/resume)
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{0.8in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\titleformat{\subsection}{
  \vspace{-4pt}\raggedright\large\bfseries
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

\begin{document}

\begin{center}
    \textbf{\Huge Veenayak Sirohi} \\ \vspace{8pt}
    \small \faIcon{phone}\href{tel:+917302223304}{\underline{+91 7302223304}} $  $
    \faMapMarker*\href{https://maps.app.goo.gl/f7FABi82qTye3gzH8}{\underline{Greater Noida,U.P}} $  $
    \faIcon{linkedin}\href{https://www.linkedin.com/in/veenayak-sirohi-ab30ab227}{\underline{linkedin/veenayak-sirohi}} $  $
    \faIcon{github}\href{https://github.com/veenayaksirohi}{\underline{github.com}} $  $
    \faIcon{envelope}\href{mailto:veenayaksirohi@gmail.com}{\underline{veenayaksirohi@gmail.com}}
\end{center}

\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{Computer Science graduate with strong \textbf{analytical} and \textbf{problem-solving} abilities. Experienced in \textbf{software development}, \textbf{data analysis}, and \textbf{web technologies}. Eager to contribute technical expertise to \textbf{innovative projects} and \textbf{business solutions}.}
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {G.L. Bajaj Group of Institutions}{}
      {Bachelor of Technology (B.Tech), Computer Science}{2021--2025}
    \resumeSubheading
      {Dewan Public School}{}
      {Schooling}{2019--2021}
  \resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, C/C++, SQL, HTML, CSS, JavaScript \\
     \textbf{Tools:} Power BI, MySQL, PostgreSQL, Excel, VS Code \\
     \textbf{Libraries:} Pandas, NumPy, Matplotlib
    }}
 \end{itemize}

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Netflix Clone Landing Page} $|$ \footnotesize\emph{HTML, CSS, JavaScript}}{2025}
          \resumeItemListStart
            \resumeItem{\textbf{Description:} Built a responsive Netflix landing page clone with interactive UI components and modern design.}
            \resumeItem{\textbf{Responsibilities:} Implemented FAQ accordion, language picker, trending content display, and mobile-responsive layout.}
            \resumeItem{\textbf{Key Features:} Interactive FAQ section, multi-language support, trending shows carousel, and smooth animations.\\}
            \resumeItem{\textbf{Achievement:} Delivered a pixel-perfect clone with accessibility features and cross-browser compatibility.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{HR Analytics Dashboard} $|$ \footnotesize\emph{Power BI, Data Cleaning and Transformation (Power Query), DAX}}{2024}
          \resumeItemListStart
            \resumeItem{\textbf{Description:} Developed an interactive dashboard to analyze employee attrition across multiple dimensions.}
            \resumeItem{\textbf{Responsibilities:} Designed visualizations that improved HR's ability to identify attrition trends by 20\%.}
            \resumeItem{\textbf{Key Metrics:} Analyzed attrition by age group, job role, salary, and education field and other key factors.}
            \resumeItem{\textbf{Outcome:} Provided insights that led to improved employee retention.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Job Market Insights: Skills and Salaries} $|$ \footnotesize\emph{Python, pandas, matplotlib}}{2025}
          \resumeItemListStart
            \resumeItem{\textbf{Description:} Conducted exploratory data analysis on 10,000+ job postings to evaluate salary distributions and skill demand.}
            \resumeItem{\textbf{Responsibilities:} Performed data cleaning, visualized salary distributions, and analyzed trends in skill sets.}
            \resumeItem{\textbf{Outcome:} Provided insights to guide strategic upskilling.}
            \resumeItem{\textbf{Achievement:} Identified the optimal skill balancing high demand and pay.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Internship}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://www.impressico.com/}{Impressico Business Solutions}} $|$ \footnotesize\emph{Intern (on-site)}}{Apr 2025 - Jun 2025}
          \resumeItemListStart
            \resumeItem{\textbf{Description:} Developed backend systems using \textbf{Flask} and \textbf{Python} for scalable web applications.}
            \resumeItem{\textbf{Responsibilities:} Designed \textbf{RESTful APIs}, integrated third-party services, optimized \textbf{PostgreSQL} queries, and implemented testing with \textbf{pytest}.}
            \resumeItem{\textbf{Achievement:} Deployed applications using \textbf{Docker} and established \textbf{CI/CD pipelines} with GitHub Actions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Licenses \& Certifications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
    \small{\item \textbf{Programming, Data Structures And Algorithms Using Python:} NPTEL}
    \small{\item \textbf{SQL For DATA SCIENCE:} Great Learning}
    \small{\item \textbf{Introduction to Microsoft Excel:} Coursera}
\end{itemize}

\end{document}